---
title: "Untitled"
author: "Hassen Allegue"
date: "12/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}

# load libraries and read data
library(data.table)
library(ggplot2)

NR <- 10
data_file_path_in  <- paste0("C:/Users/HASSEN/Documents/MS3_squid_data/fit_model_data/MS3_fit_model_data_NR_", NR,".csv")
param_file_path_in <- paste0("C:/Users/HASSEN/Documents/MS3_squid_data/simulated_data/MS3_parameters_NR_", NR,".csv")

fit_data <- fread(data_file_path_in)
# setnames(fit_data, c("Ve"), c("Vw"))

parameters <- fread(param_file_path_in)
setnames(parameters, c("VI", "Ve"), c("VI_true", "Ve_true"))

# combine fitted results and input parameters 
setkey(fit_data, Sim_id); setkey(parameters, Sim_id);
fit_data <- merge(fit_data, parameters[ , .(VI_true, Ve_true, e_corr, Vhsi, X1_sto_shared, X1_sto_corr, X1_lin_state, X1_cyc_state, VE, Sim_id)], by="Sim_id")



fit_data <- melt(fit_data, id.vars = c("Sim_id", "Replicate", "Model", "VI_true", "Ve_true", "e_corr", "Vhsi", "X1_sto_shared", "X1_sto_corr", "X1_lin_state", "X1_cyc_state", "VE"), measure.vars = c("VI", "Ve"))


fit_data[ , X1_lin_state  := factor(ifelse(X1_lin_state, "Linear", "Not linear"), levels = c("Not linear", "Linear"))]
fit_data[ , X1_cyc_state  := factor(ifelse(X1_cyc_state, "Cyclic", "Not cyclic"), levels = c("Not cyclic", "Cyclic"))]
fit_data[ , X1_sto_shared := factor(ifelse(X1_sto_shared, "Shared", "Unshared"), c("Shared", "Unshared"))]

setnames(fit_data, c("variable", "value"), c("variable_est", "value_est"))

fit_data[variable_est == "VI",  value_true := VI_true]
fit_data[variable_est == "Ve",  value_true := Ve_true]


fit_data[ , VI_true_string := paste0("VI = ", VI_true)]

fit_data[variable_est == "Ve", Vw_true := VE + value_true]


# fit_data[ , Vw_true := 1 - VI_true]
# fit_data[variable_est == "Vw", value_true := Vw_true]

fit_data[ , Model := factor(Model, levels = c("null", 
                                              "time.fixed",
                                              "time.random",
                                              "Id.period.random",
                                              "time_between_mc",
                                              "time_within_mc",
                                              "time_between_within_mc",
                                              "lme.corAR1",
                                              "lme.corExp"))]

```


```{r plot-function, message=FALSE, warning=FALSE, include=FALSE}

plot_fig <- function(dt, corr="X1_sto_corr", corr_label="Autocorrelation in X"){

  p <- ggplot(data = dt, aes(x=as.factor(Vhsi), y=value_est, color=as.factor(dt[[corr]]))) +
          geom_boxplot() + 
          geom_hline(aes(yintercept  = value_true)) +
          geom_hline(aes(yintercept  = Vw_true), linetype="dotted", color="red") +
          facet_grid(Model ~ VI_true_string + variable_est) +
          scale_color_discrete(name = corr_label) +
          ylab("Variance value") + xlab("Among-individual variance in sampling") +
          theme_bw() + 
          theme(legend.position = "top",
                strip.text.y    = element_text(size = 8),
                axis.text.x     = element_text(angle = 67.5, hjust = 1, size = 7))
  
  print(p)
}

```


# Shared / X stochastic / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Not linear" & X1_cyc_state == "Not cyclic" & X1_sto_shared == "Shared" & e_corr == 0])

```

# Shared / X Linear / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Linear" & X1_cyc_state == "Not cyclic" & X1_sto_shared == "Shared" & e_corr == 0])

```

# Shared / X Cyclic / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Not linear" & X1_cyc_state == "Cyclic" & X1_sto_shared == "Shared" & e_corr == 0])

```

# Shared / X Linear and Cyclic / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Linear" & X1_cyc_state == "Cyclic" & X1_sto_shared == "Shared" & e_corr == 0])

```

# Unshared / X stochastic / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Not linear" & X1_cyc_state == "Not cyclic" & X1_sto_shared == "Unshared" & e_corr == 0])

```

# Unshared / X Linear / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Linear" & X1_cyc_state == "Not cyclic" & X1_sto_shared == "Unshared" & e_corr == 0])

```

# Unshared / X Cyclic / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Not linear" & X1_cyc_state == "Cyclic" & X1_sto_shared == "Unshared" & e_corr == 0])

```

# Unshared / X Linear and Cyclic / No correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Linear" & X1_cyc_state == "Cyclic" & X1_sto_shared == "Unshared" & e_corr == 0])

```

# Shared / X stochastic and without correlation / Correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Not linear" & X1_cyc_state == "Not cyclic" & X1_sto_shared == "Shared" & X1_sto_corr == 0], corr="e_corr", corr_label="Autocorrelation in residuals")

```

# Unshared / X stochastic and without correlation / Correlation in residuals

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=15, fig.width=12}

plot_fig(fit_data[X1_lin_state == "Not linear" & X1_cyc_state == "Not cyclic" & X1_sto_shared == "Unshared" & X1_sto_corr == 0], corr="e_corr", corr_label="Autocorrelation in residuals")

```



