---
title: "Code for Analysis"
output:
  html_document:
    keep_md: true
---

This code was used for the analysis of the paper:

Denis et al. (2025) **Avoiding misleading estimates of among-individual variance caused by non-random sampling of individuals in a changeable environment**. Methods Ecol. Evol.

## Getting Started

To reproduce the analyses, follow these steps:

1. Install R and Rtools
 * [`R` 4.1.3](https://cran.r-project.org/bin/windows/base/old/)
 * [`Rtools40`](https://cran.r-project.org/bin/windows/Rtools/) 

2. Set up the reproducible environment

Install the `{renv}` package (if not already installed)

```{r eval=FALSE}
install.packages("renv")
```

Then from the root of this project:
```{r eval=FALSE}
renv::restore()
```

This will install all required package dependencies as specified in the `renv.lock` file.

3. Run the analysis

Execute the main workflow by running:

```{r eval=FALSE}
source("run.R")
```

The pipeline is managed with the [`{targets}`](https://books.ropensci.org/targets/) package. This ensures analyses are fully reproducible and results are built following declared dependencies.

## Notes

* Ensure your working directory is set to the root of the project before running scripts.
* All package versions are pinned via `{renv}` to guarantee reproducibility.